---
title: "In season estimation of EONR"
author: "Morteza Abdipourchenarestansofla"
date: "2024-02-14"
output: html_document
---



```{r}


library(sf)
library(rsm)
library(broom)
library(ggplot2)
options(scipen = 1000)
```


# Read data
```{r}

base_dir = getwd()

data_dir = paste0(base_dir, "/", "data_maplayers_one_field.csv")

data_wkt <- st_read(data_dir, options = "GEOM_POSSIBLE_NAMES=WKT")
maplayers_sf <- data_wkt[,!(names(data_wkt) == "WKT")] 
st_crs(maplayers_sf) <- st_crs("+proj=utm +zone=32 +datum=WGS84 +units=m +no_defs")


## Covert datatype to numeric
maplayers_sf[, sapply(maplayers_sf, is.character)] <- lapply(maplayers_sf[, sapply(maplayers_sf, is.character)], as.numeric)

maplayers_df = sf::st_drop_geometry(maplayers_sf)




```
# Yield-applied N relationship using Quadratic function
```{r}

#### Wet-Mass vs applied_rate, N-treatment
ggplot(maplayers_df, aes(x = applied_rate, y=wet_mass_idw)) + geom_point(size=3)  +
                      geom_smooth(method = "lm", formula = y ~ poly(x,2), se=FALSE) + 
                      ggtitle("quadratic regression") + xlab("N-applied, kg/ha") + ylab("harvested grain, kg/ha")

```




### Filter the best identified multispectral indicess during feature selection process using ANOVA and Lasso regression.

```{r}

candidate_VIs = c(
                'cloud.coverage.0_CARI2_2020.03.25.10.36.59_7632',
                'cloud.coverage.0_LCI_2020.03.25.10.36.59_7632',
                'cloud.coverage.0_ARI2_2020.03.25.10.36.59_7632',
                'cloud.coverage.0_CRI550_2020.03.25.10.36.59_7632',
                'cloud.coverage.0_EVI_2020.03.25.10.36.59_7632',
                
                 'cloud.coverage.0_CARI_2020.03.30.10.37.00_8331',
                'cloud.coverage.0_CARI2_2020.03.30.10.37.00_8331',
                'cloud.coverage.0_CRI550_2020.03.30.10.37.00_8331',
                'cloud.coverage.0_NDRE_2020.03.30.10.37.00_8331',
                
                'cloud.coverage.0_CARI2_2020.04.04.10.36.59_1536',
                'cloud.coverage.0_LCI_2020.04.04.10.36.59_1536',
                'cloud.coverage.0_CRI550_2020.04.04.10.36.59_1536',
                'cloud.coverage.0_CRI700_2020.04.04.10.36.59_1536',
                'cloud.coverage.0_NDRE_2020.04.04.10.36.59_1536',
                "applied_rate",
                "wet_mass_idw")




candidate_VIs_df = subset(maplayers_df, select = candidate_VIs)


```


# Modeling with RSM

```{r}

reduced_model_formula = wet_mass_idw ~ SO(applied_rate,
                        cloud.coverage.0_CARI2_2020.03.25.10.36.59_7632,
                        cloud.coverage.0_ARI2_2020.03.25.10.36.59_7632,
                        
                        cloud.coverage.0_CARI_2020.03.30.10.37.00_8331,
                        cloud.coverage.0_CRI550_2020.03.30.10.37.00_8331,
                        
                        cloud.coverage.0_CARI2_2020.04.04.10.36.59_1536,
                        cloud.coverage.0_CRI700_2020.04.04.10.36.59_1536)




full_model <- rsm(reduced_model_formula, data = candidate_VIs_df)
mdl_summary = summary(full_model)
mdl_summary
```
# Regression diagnostic plots

```{r}

augmented_data <- augment(full_model)

# Residuals vs Fitted plot
ggplot(data = augmented_data, aes(.fitted, .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  ggtitle("Residuals vs Fitted") +
  xlab("Fitted Values") +
  ylab("Residuals") + labs(title = "Residuals vs Fitted Plot - Best-model")

# Normal Q-Q plot of residuals
ggplot(data = augmented_data, aes(sample = .std.resid)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("Normal Q-Q Plot of Residuals") + labs(title = "Normal Q-Q plot of residuals - Best-model")




```
## Compute model accuracy. RMSE percentage

```{r}

# Calculate the squared differences between actual and predicted values
squared_errors <- (candidate_VIs_df$wet_mass_idw - full_model$fitted.values)^2

# Calculate the mean of squared errors
mean_squared_error <- mean(squared_errors)

# Calculate the RMSE (take the square root of the mean squared error)
rmse <- sqrt(mean_squared_error)

(rmse/mean(candidate_VIs_df$wet_mass_idw)) * 100



```




## Compute N-opt
```{r}


compute_n_opt = function(trainmodel, first.date.CARI2, first.date.ARI2, second.date.CARI, second.date.CRI550, third.date.CARI2, third.date.CRI700){
  
  
  mdl_summary = summary(trainmodel)
  # collected_terms = mdl_summary$coefficients[c(1:14, 30:36), ]
  
#######################################################################
    ### Linear terms plus estimated coefficient for N
    # c.0 = mdl_summary$coefficients[c(1, 3:8),]
#######################################################################  
  
  first_date_CARI2 = mdl_summary$coefficients[3] * first.date.CARI2
  
  first_date_ARI2 = mdl_summary$coefficients[4] * first.date.ARI2
  
  second_date_CARI = mdl_summary$coefficients[5] * second.date.CARI
  
  second_date_CRI550 = mdl_summary$coefficients[6] * second.date.CRI550
  
  third_date_CARI2 = mdl_summary$coefficients[7] * third.date.CARI2

  third_date_CRI700 = mdl_summary$coefficients[8] * third.date.CRI700

  c.0 =  mdl_summary$coefficients[1] + first_date_CARI2 + first_date_ARI2 + second_date_CARI + second_date_CRI550 + third_date_CARI2 + third_date_CRI700
  
  

#######################################################################
    ### Interaction terms plus estimated coefficient for N
    # C.1 = mdl_summary$coefficients[c(2, 9:14)]
#######################################################################  
  
  first_date_CARI2_interaction = mdl_summary$coefficients[9] * first.date.CARI2
  
  first_date_ARI2_interaction = mdl_summary$coefficients[10] * first.date.ARI2
  
  second_date_CARI_interaction = mdl_summary$coefficients[11] * second.date.CARI
  
  second_date_CRI550_interaction = mdl_summary$coefficients[12] * second.date.CRI550

  
  third_date_CARI2_interaction = mdl_summary$coefficients[13] * third.date.CARI2

  third_date_CRI700_interaction = mdl_summary$coefficients[14] * third.date.CRI700
  
  c.1 =  mdl_summary$coefficients[2] +  first_date_CARI2_interaction + first_date_ARI2_interaction + second_date_CARI_interaction + second_date_CRI550_interaction + third_date_CARI2_interaction + third_date_CRI700_interaction
  

  c.2 =  mdl_summary$coefficients[30]


  n_opt = (0.417/0.318) * (1/(2*c.2)) - (c.1/ (2*c.2))
  
  
  
  if(class(n_opt)== "data.frame"){
    
    
    names(n_opt) = "optimum_nitrogen"
    names(c.0) = "intercept"
    names(c.1) = "interaction_terms"


    n_opt$intercept = c.0$intercept
    n_opt$interaction = c.1$interaction_terms

    
    }
  
  
  return(n_opt)
  
  
  
}










#####################################################################################
################### Prediction of EONR ############################################
#####################################################################################



final_vis_predictors = c("cloud.coverage.0_CARI2_2020.03.25.10.36.59_7632", 
                        "cloud.coverage.0_ARI2_2020.03.25.10.36.59_7632", 
                         "cloud.coverage.0_CARI_2020.03.30.10.37.00_8331",
                        "cloud.coverage.0_CRI550_2020.03.30.10.37.00_8331", 
                        "cloud.coverage.0_CARI2_2020.04.04.10.36.59_1536", 
                        "cloud.coverage.0_CRI700_2020.04.04.10.36.59_1536")


VIs_predictors_df = candidate_VIs_df[, final_vis_predictors]


n_inpute = compute_n_opt(trainmodel = full_model, 
             first.date.CARI2 = VIs_predictors_df[1], first.date.ARI2 = VIs_predictors_df[2],
             second.date.CARI = VIs_predictors_df[3], second.date.CRI550 = VIs_predictors_df[4],
             third.date.CARI2 = VIs_predictors_df[5], third.date.CRI700 = VIs_predictors_df[6])


hist(n_inpute$optimum_nitrogen,  main = "Economic optimum N rate", xlab = "N-kg/ha")
hist(candidate_VIs_df$applied_rate)

```

```{r}

sf_final_data <- subset(maplayers_sf, select = final_vis_predictors)

sf_final_data$optimum_n = n_inpute[, 'optimum_nitrogen']

# Define a color palette with red, yellow, and green
color_palette <- colorRampPalette(c("red", "yellow", "green"))

# Create map view with continuous color scale
mapview::mapview(sf_final_data, zcol = "optimum_n", col.regions = color_palette,
        legend = TRUE, legend.style = "classic")

```



# Calculate Total N
```{r}

sf_final_data$optimum_n_total_N = sf_final_data$optimum_n  / 0.26


# Define a color palette with red, yellow, and green
color_palette <- colorRampPalette(c("red", "yellow", "green"))

# Create map view with continuous color scale
mapview::mapview(sf_final_data, zcol = "optimum_n_total_N", col.regions = color_palette,
        legend = TRUE, legend.style = "classic")


```



# Plot two points with different EONR

The location indexes we used for visualization purpose are as follows,
1 and 1800

```{r}

c_value_0 <- n_inpute$intercept[1]
c_value_1 <-n_inpute$interaction[1]
c_value_2 <- mdl_summary$coefficients[30]

# Single value N
N <- seq(30, 90, length.out = 100)

# Quadratic function
Y <- c_value_0 + c_value_1 * N + c_value_2 * N^2


# Calculate N for the maximum
N_max <- -c_value_1 / (2 * c_value_2)

# Calculate corresponding f(N) for the maximum
Y_max <- c_value_0 + c_value_1 * N_max + c_value_2 * N_max^2

# Plot the curve
plot(N, Y, type = "l", col = "blue", xlab = "N kg/ha", ylab = "Y(N) kg/ha", main = "Quadratic Function")

# Add a vertical line at the maximum
abline(v = N_max, col = "red", lty = 2)

# Add a legend
legend("bottomright", legend = expression(Y(N) == c[0] + c[1] * N + c[2] * N^2), col = "blue", lty = 1)

# Add text annotations for c_value_0, c_value_1, and c_value_2
text(N[1], Y[1], paste("c[0] =", round(c_value_0, 2)), pos = 4, col = "black")
text(N[50], Y[50], paste("c[1] =", round(c_value_1, 2)), pos = 2, col = "black")
text(N[80], Y[80], paste("c[2] =", round(c_value_2, 2)), pos = 1, col = "black")

# Print the results
cat("N for maximum:", N_max, "\n")
cat("Maximum value Y(N):", Y_max, "\n")


c_value_0
c_value_1
c_value_2
```
```{r}

c_value_0 <- n_inpute$intercept[1800]
c_value_1 <-n_inpute$interaction[1800]
c_value_2 <- mdl_summary$coefficients[30]

# Single value N
N <- seq(30, 90, length.out = 100)

# Quadratic function
Y <- c_value_0 + c_value_1 * N + c_value_2 * N^2


# Calculate N for the maximum
N_max <- -c_value_1 / (2 * c_value_2)

# Calculate corresponding f(N) for the maximum
Y_max <- c_value_0 + c_value_1 * N_max + c_value_2 * N_max^2

# Plot the curve
plot(N, Y, type = "l", col = "blue", xlab = "N kg/ha", ylab = "Y(N) kg/ha", main = "Quadratic Function")

# Add a vertical line at the maximum
abline(v = N_max, col = "red", lty = 2)

# Add a legend
legend("bottomright", legend = expression(Y(N) == c[0] + c[1] * N + c[2] * N^2), col = "blue", lty = 1)

# Add text annotations for c_value_0, c_value_1, and c_value_2
text(N[1], Y[1], paste("c[0] =", round(c_value_0, 2)), pos = 4, col = "black")
text(N[50], Y[50], paste("c[1] =", round(c_value_1, 2)), pos = 2, col = "black")
text(N[80], Y[80], paste("c[2] =", round(c_value_2, 2)), pos = 1, col = "black")

# Print the results
cat("N for maximum:", N_max, "\n")
cat("Maximum value Y(N):", Y_max, "\n")


c_value_0
c_value_1
c_value_2
```


# Plot a bundle of points. 

Picking a few locations in the field and ploting the N-yield response. 

Candidate locations are 1, 1800, 100, 200, 56, and 440.


```{r}

c_0 <- n_inpute$intercept
c_1 <-n_inpute$interaction
c_2 <- mdl_summary$coefficients[30]

c_0_subset = c_0[c(1, 1800, 100, 200, 56, 440)]
c_1_subset = c_1[c(1, 1800, 100, 200,  56, 440)]

c_values_0 <- c_0_subset
c_values_1 <-c_1_subset
c_value_2 <- c_2

# Single value N
N <- seq(0, 100, length.out = 400)

# Create an empty plot with specified ylim
plot(N, rep(NA, length(N)), type = "n", col = "white", xlab = "N kg/ha", ylab = "Y(N) kg/ha", main = "Quadratic Functions", ylim = c(1000, 12000))

# Plot the curves
for (i in 1:length(c_values_0)) {
  c_value_0 <- c_values_0[i]
  c_value_1 <- c_values_1[i]
  
  # Quadratic function
  f <- c_value_0 + c_value_1 * N + c_value_2 * N^2
  
  # Add the curve to the plot
  lines(N, f, col = i + 1)  # Use different colors for each curve
}

# Add a legend
legend("topright", legend = c(expression(Y(N) == c[0] + c[1] * N + c[2] * N^2), paste("Set ", 2:5)), col = 2:(length(c_values_0) + 1), lty = 1)

```

